Synthesizing Quotient Lenses

### 2018-03-14 papers/QuotientLenses/main.tex
updated Figure 5

Figure~\ref{fig:canonizers} gives the inductive definitions of the
$\canonize{}$ function for each QRE.
\begin{figure}[t]
\begin{center}
\[
\begin{array}{l@\quad l @\quad l}
\canonize(\id(R))(w) &=& w \\
\canonize(\collapse{R}{s})(w) &=& s\\[1ex]
\canonize(\squash{Q_1}{Q_2}{f})(w) &=&
\begin{cases}
\canonize(Q_1)(f(w)) & \text{if } w \in \mathcal{L}(W(Q_1))\\
\canonize(Q_2)(w) & \text{otherwise}
\end{cases}\\[3ex]
\canonize(\normalize{R_1}{R_2}{f}) &=& f\\
\canonize(Q_1 \; ; \; Q_2) &=& \canonize(Q_2) \circ \canonize(Q_1)\\
\canonize(Q_1 \cdot Q_2)(w_1 \cdot w_2) &=& \canonize(Q_1)(w_1) \cdot \canonize(Q_2)(w_2)\\[1ex]
\canonize(Q_1 \sep Q_2)(w) &=&
\begin{cases}
\canonize(Q_1)(w) & \text{if } w \in \mathcal{L}(W(Q_1))\\
\canonize(Q_2)(w) & \text{if } w \in \mathcal{L}(W(Q_2))\\
\end{cases}\\[3ex]
\canonize(Q^*)(\epsilon) &=& \epsilon \\
\canonize(Q^*)(w_1 \cdot w_2) &=& \canonize(Q)(w_1)\cdot\canonize(Q^*)(w_2) \\
\end{array}
\]
\end{center}
\begin{align*}
&\canonize(\perm{Q_1, \ldots, Q_n}{Q})(r_{\sigma(1)}
\cdot s_1 \cdot \ldots \cdot s_{n-1} \cdot r_{\sigma(n)})\\
&= (\canonize(Q_1)(r_1)) \cdot (\canonize(Q)(s_1)) \cdot \ldots \cdot
(\canonize(Q)(s_{n-1}))\cdot
(\canonize(Q_n)(r_n))
\end{align*}
\caption{QRE canonizers. \ksf{Solomon: please define/explain the . and *
operators on functions.}\afm{I tried rewriting with explicit arguments,
thoughts?}\saz{If so, do it consistently everywhere. I fixed \id{} but the
others need to be fixed too.}}
\label{fig:canonizers}
\end{figure}
The \kw{permutation} combinator gives rise to the most interesting
definition:
\[
\begin{array}{cl}
 & \canonize(\perm{Q_1, \ldots, Q_n}{Q})(r_{\sigma(1)}
\cdot s_1 \cdot \ldots \cdot s_{n-1} \cdot r_{\sigma(n)}) \\
= & (\canonize(Q_1)(r_1)) \cdot (\canonize(Q)(s_1)) \cdot \ldots \cdot
(\canonize(Q)(s_{n-1}))\cdot
(\canonize(Q_n)(r_n))
\end{array}
\]
\noindent 
which places the strings that match $Q_i$ and $Q$ according to the
canonical permutation (i.e., the identity permutation) before applying
the canonizers $\canonize(Q_i)$ and $\canonize(Q)$, respectively.

>>>>

Figure~\ref{fig:canonizers} gives the inductive definitions of the
$\canonize{}$ function for each QRE.
\begin{figure}[t]
\begin{center}
\[
\begin{array}{l@\quad l @\quad l}
\canonize(\id(R))(w) &=& w \\
\canonize(\collapse{R}{s})(w) &=& s\\[1ex]
\canonize(\squash{Q_1}{Q_2}{f})(w) &=&
\begin{cases}
\canonize(Q_1)(f(w)) & \text{if } w \in \mathcal{L}(W(Q_1))\\
\canonize(Q_2)(w) & \text{otherwise}
\end{cases}\\[3ex]
\canonize(\normalize{R_1}{R_2}{f})(w) &=& f(w)\\
\canonize(Q_1 \; ; \; Q_2)(w) &=& \canonize(Q_2)(\canonize(Q_1)(w))\\
\canonize(Q_1 \cdot Q_2)(w_1 \cdot w_2) &=& \canonize(Q_1)(w_1) \cdot \canonize(Q_2)(w_2)\\[1ex]
\canonize(Q_1 \sep Q_2)(w) &=&
\begin{cases}
\canonize(Q_1)(w) & \text{if } w \in \mathcal{L}(W(Q_1))\\
\canonize(Q_2)(w) & \text{if } w \in \mathcal{L}(W(Q_2))\\
\end{cases}\\[3ex]
\canonize(Q^*)(\epsilon) &=& \epsilon \\
\canonize(Q^*)(w_1 \cdot w_2) &=& \canonize(Q)(w_1)\cdot\canonize(Q^*)(w_2) \\[2ex]
\multicolumn{3}{l}{\canonize(\perm{Q_1, \ldots, Q_n}{Q})(r_{\sigma(1)}
\cdot s_1 \cdot \ldots \cdot s_{n-1} \cdot r_{\sigma(n)})(w_{\sigma(1)} \cdot s_1
  \cdot \ldots \cdot s_{n-1} \cdot w_{\sigma(n)})}\\[.5ex]
\multicolumn{3}{l}{\ =\ \ (\canonize(Q_1)(r_1))(w_1) \cdot (\canonize(Q)(s_1)) \cdot \ldots \cdot
(\canonize(Q)(s_{n-1}))\cdot(\canonize(Q_n)(r_n))(w_n)}
\end{array}
\]
\end{center}
\caption{QRE canonizers.  Here we assume that the input $w$ to the canonizers
  has been partitioned in the unique way guaranteed to exist by the lens unambiguity conditions.}
\label{fig:canonizers}
\end{figure}
The \kw{permutation} combinator gives rise to the most interesting
definition:
\[
\begin{array}{cl}
 & \canonize(\perm{Q_1, \ldots, Q_n}{Q})(r_{\sigma(1)}
\cdot s_1 \cdot \ldots \cdot s_{n-1} \cdot r_{\sigma(n)}) \\
= & (\canonize(Q_1)(r_1)) \cdot (\canonize(Q)(s_1)) \cdot \ldots \cdot
(\canonize(Q)(s_{n-1}))\cdot
(\canonize(Q_n)(r_n))
\end{array}
\]
\noindent 
which places the strings that match $Q_i$ and $Q$ according to the
canonical permutation (i.e., the identity permutation) before applying
the canonizers $\canonize(Q_i)$ and $\canonize(Q)$, respectively.
